---
title: "VideoGames_Analysis"
author: "Ahmed ALRashid"
date: "10/17/2020"
output: html_document
---

```{r include=FALSE}
library(tidyverse)
library(DT)
vgSales <- read.csv("data/vgsales.csv")

```

# Introduction

Discuss the data and where it came from [kaggle](https://www.kaggle.com/gregorut/videogamesales)

# Research questions

With this data set we'll attempt to uncover ....

(What are the kinds of research question that you can answer with this data set?). Is there a relationship between region and platforms, or genres? Have specific genres increased of decreased in popularity over time. Are certain genres more popular on certain platforms, etc. 

What about the rankings?


# Video Games Sales top 10 globaly 

```{r}
GS_top10 <- vgSales %>% 
  summarise(vgSales, Global_Sales) %>% 
  top_n(10)
datatable(GS_top10)
  
```


# Plot showing the global sales based on platform 

```{r}
sort(unique(vgSales$Year))

# Select only certain platforms
# choose only one year ()

vgSales %>% 
  filter(Year == "2015", Platform %in% c("Wii", "NES", "3DS")) %>% 
  group_by(Platform, Genre) %>% 
  summarise(Total_Sales = sum(Global_Sales)) %>% 
  ggplot(aes(Genre, Total_Sales, fill = Platform)) +
  geom_col()

```



```{r}
ggplot(vgSales, aes(Platform, Global_Sales, color = "region")) +
  geom_bar(stat = "identity") +
   theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none")
        
```




# Number of games per publisher 

```{r}
nGames <- vgSales %>% 
  group_by(Publisher) %>%
 count(sort = TRUE)

datatable(nGames)

```


# Top sold game for each platform

incomplete

```{r}
top_g <- vgSales %>% 
  group_by_(Platform)
  
```
